\bf Visualising How Non-linear Dimension Reduction Warps Your Data

### 2024-01-17 paper.qmd
Added kang dataset example with tSNE, fix the error of getting PCAs in PBMC3k data set, complete the tour generation code for PBMC3k (need to record the video)

@@

load("data/pbmc/pbmc_3k_festem/pbmc3k_label.RData")

@@

class_avg <- UMAP_pbmc |>
  group_by(cell_label) |>
  summarise(
    UMAP1 = median(UMAP1),
    UMAP2 = median(UMAP2)
  )

@@

>>>>

https://github.com/XiDsLab/Festem_paper/tree/main

@Chen2023

@@

#load("data/pbmc/pbmc_3k_festem/pbmc3k_label.RData")

@@

class_avg <- UMAP_pbmc |>
  group_by(cell_label) |>
  summarise(
    UMAP1 = median(UMAP1),
    UMAP2 = median(UMAP2)
  ) |>
  mutate(cell_label = as.numeric(cell_label)) |>
  arrange(cell_label)

@@

### Kang dataset

## Import data
#df_2 <- read_rds("data/pbmc/pbmc.rds")
# training_data_1 <- read_rds("data/pbmc/pbmc_3k_festem/pbmc_pca_50.rds")
# training_data_1 <- training_data_1[, 1:25]
#test_1 <- read_rds("data/pbmc/pbmc_test.rds")

#tSNE_pbmc <- read_rds("data/pbmc/pbmc_tsne_30.rds")
tSNE_kang <- read_rds("data/kang/kang_tsne.rds") |>
  mutate(cell_label = if_else(cell_label %in% c("0", "3", "5"), "0", cell_label))
# PHATE_pbmc <- read_rds("data/pbmc/pbmc_phate.rds")
# TriMAP_pbmc <- read_rds("data/pbmc/pbmc_trimap.rds")
# PaCMAP_pbmc <- read_rds("data/pbmc/pbmc_pacmap.rds")

#load("data/pbmc/pbmc_3k_festem/pbmc3k_label.RData")

class_avg <- tSNE_kang |>
  group_by(cell_label) |>
  summarise(
    tSNE1 = median(tSNE1),
    tSNE2 = median(tSNE2)
  ) |>
  mutate(cell_label = as.numeric(cell_label)) |>
  arrange(cell_label)

levels(class_avg$cell_label) <- c("CD14 Monocyte", "CD4 \n Memory T", "CD4 Naive T", "CD16 Monocyte", "B", "T Activated", "CD8 T", "NK", "DC", "B \nActivated", "T cell:\nmonocyte \nComplex", "HSP+ CD4 T", "IFN^hi CD14 \n Monocyte", "CD34 \n Progenitors", "pDC")

plot_list2_kang <- tSNE_kang |>
    ggplot(aes(x = tSNE1,
               y = tSNE2, color = cell_label))+
    geom_point(alpha=0.5) +
    coord_equal() +
    theme(plot.title = element_text(hjust = 0.5, size = 18, face = "bold")) + #ggtitle("(a)") +
  theme_linedraw() +
    theme(legend.position = "none", plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
              axis.title.x = element_blank(), axis.title.y = element_blank(),
              axis.text.x = element_blank(), axis.ticks.x = element_blank(),
              axis.text.y = element_blank(), axis.ticks.y = element_blank(),
              panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=5), #change legend title font size
        legend.text = element_text(size=4),
         legend.key.height = unit(0.25, 'cm'),
         legend.key.width = unit(0.25, 'cm')) +
  scale_color_manual(values=c("#b15928", "#1f78b4", "#b2df8a", "#33a02c", "#fb9a99", "#e31a1c", "#6a3d9a", "#ff7f00", "#cab2d6", "#fdbf6f", "#ffff99", "#a6cee3", "#8dd3c7", "#ffffb3", "#bebada", "#fb8072", "#80b1d3", "#fdb462", "#b3de69", "#fccde5", "#d9d9d9", "#bc80bd", "#ccebc5", "#ffed6f", "#000000", "#bdbdbd")) +
  geom_text(aes(x=tSNE1,y = tSNE2,label = cell_label), data = class_avg,inherit.aes = F, color = "black",fontface = "bold",size = 2) #+
  # guides(color = guide_legend(title = "Cell type"),
  #        color = guide_legend(nrow = 3)) #+
  # annotate(geom = 'text', label = 'b', x = Inf, y = Inf, hjust = 1.5, vjust = 1.5, size = 3)

```{r}
#| echo: false
#| fig-cap: "2D layout from tSNE (perplexity = 30) applied for the Kang dataset. Is this a best representation of the original data?"
#| label: fig-nlderviskangtSNE

plot_list2_kang

### 2024-01-17 paper.tex
Added kang dataset example with tSNE, fix the error of getting PCAs in PBMC3k data set, complete the tour generation code for PBMC3k (need to record the video)

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, frame hidden, sharp corners, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, interior hidden, enhanced]}{\end{tcolorbox}}\fi

@@

@@

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, interior hidden, borderline west={3pt}{0pt}{shadecolor}, frame hidden, breakable, sharp corners, enhanced]}{\end{tcolorbox}}\fi

@@

https://github.com/XiDsLab/Festem\_paper/tree/main

\citet{Chen2023}

@@

\hypertarget{kang-dataset}{%
\subsection{Kang dataset}\label{kang-dataset}}

{\centering \includegraphics{paper_files/figure-pdf/fig-nlderviskangtSNE-1.pdf}

\caption{\label{fig-nlderviskangtSNE}2D layout from tSNE (perplexity =
30) applied for the Kang dataset. Is this a best representation of the
original data?}
